\huge \textbf{Parameter Forecasts From CMB Lensing and Galaxy Lensing Power- and Bispectra}

### 2025-05-07 paper/paper_draft.tex
fixed fisher manip

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par            &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$          &        9.8607392131 &     1.9228760331 &        5.0596593228 &        4.9998059321 &              0.6566865031 \\
         $\Omega_b h^2$ &       21.1047938757 &    22.3422408475 &        9.9278715395 &       19.0626128005 &              6.6783756779 \\
         $\Omega_c h^2$ &        0.0000125702 &     1.9971113528 &        0.0000125243 &        2.4722397353 &              0.0000125239 \\
         $n_s$          &        2.5555063255 &     2.0884251995 &        1.0353938531 &        3.4233966612 &              0.6771684184 \\
         $m_\nu$        &      540.3486045452 &   397.7301866598 &      197.9074769610 &      274.0779514021 &            110.8336892534 \\
         $A_s$          &       17.8092869822 &     7.5399323519 &        4.1275268227 &        7.9422103452 &              2.0233577134 \\
         $w_0$          &       43.5247638551 &     3.8394789067 &       12.3789001621 &       13.7550208605 &              1.7287298348 \\
        \hline
        \end{tabular}
\caption{Parameter constraints in percentage of the fiducial values for different combinations of weak lensing information.}
\label{tab:paramconstraintsall}
\end{figure}

@@

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par            &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$          &        5.3683958191 &     0.8819917551 &        0.1393060101 &        0.6113966629 &              0.1212982914 \\
         $\sigma_8$     &        0.0000000157 &     0.0000000157 &        0.0000000057 &        0.0000000099 &              0.0000000046 \\
         $\Omega_b h^2$ &        5.5823437092 &     3.3491075426 &        2.8087163845 &        3.9650003059 &              2.2514916319 \\
        \hline
        \end{tabular}
\caption{Same as table \ref{tab:paramconstraintsall}, except for a smaller selection of parameters well constrained by lensing.}
\label{tab:paramconstraintstight}
\end{figure}

>>>>

\begin{figure}
    \centering
    \tiny
    \begin{tabular}{lrrrrr}
        \hline
         Par                       &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
        \hline
         $H_0$                     &              102.87 &             1.94 &                9.63 &                5.22 &                      0.94 \\
         $\Omega_b h^2$            &              234.33 &            21.39 &               25.53 &               20.30 &                     13.50 \\
         $\Omega_c h^2$            &              127.06 &             2.43 &                3.96 &                3.13 &                      1.42 \\
         $n_s$                     &               25.44 &             1.94 &                3.25 &                3.82 &                      1.51 \\
         $m_\nu$                   &             3121.97 &           307.15 &              384.96 &              277.55 &                    178.07 \\
         $A_s$                     &               69.24 &             6.39 &                7.96 &                8.44 &                      4.45 \\
         $w_0$                     &              103.74 &             2.90 &               23.14 &               13.87 &                      2.33 \\
         \hline
         \hline
         $\sigma_8$                &               31.82 &             3.85 &                9.16 &                4.56 &                      1.84 \\
         $S_8$                     &               37.67 &             2.08 &                2.52 &                2.27 &                      1.14 \\
         $\Omega_m$                &              172.99 &             5.65 &               27.29 &               14.45 &                      3.57 \\
         $\sigma_8\Omega_m^{0.25}$ &               32.15 &             2.65 &                2.82 &                1.99 &                      1.29 \\
        \hline
        \end{tabular}
\caption{Parameter constraints in percentage of the fiducial values for different combinations of weak lensing information. Below the double line are constraints for derived parameters.}
\label{tab:paramconstraintsall}
\end{figure}

@@

% \begin{figure}
%     \centering
%     \tiny
%     \begin{tabular}{lrrrrr}
%         \hline
%          Par        &   CMB + Gal Powersp &   CMB + Gal Bisp &   CMB Power- + Bisp &   Gal Power- + Bisp &   CMB + Gal Power- + Bisp \\
%         \hline
%          $H_0$      &      102.8657993427 &     1.9383910910 &        9.6317154638 &        5.2219296015 &              0.9395018958 \\
%          $\sigma_8$ &       31.8199604416 &     3.8499102909 &        9.1631304725 &        4.5639390699 &              1.8357116464 \\
%          $\Omega_m$ &      172.9940493951 &     5.6526767874 &       27.2943604041 &       14.4462387878 &              3.5663315554 \\
%         \hline
%     \end{tabular}
% \caption{Same as table \ref{tab:paramconstraintsall}, except for a smaller selection of parameters well constrained by lensing.}
% \label{tab:paramconstraintstight}
% \end{figure}
